Active Learning : From Blackbox To Timed Connectors

### 2015-12-29 paper/paper.tex
.

So far as we can tell, most works\cite{DBLP:conf/fase/RaffeltS06} on automata learning are not
capable of infinite models. \todo{reason?} Considering the semantics defined in section
\ref{sec:reo}, it's apparent that every finite connector has a corresponding constraint
automata, and the automata is also finite. Unfortunately, when checking the further definition of
Reo connectors' input, we find that it's not the case.

@@

\todo{finish the definition ..}
\begin{definition}[Production of Parameterized Mealy Machines]
  Now we're going to define the production operator \emph{prod} of two parameterized mealy machines as,
  \[
  prod(PM_1,PM_2)=PM_3
  \]
  as follows, 
  \begin{itemize}
  	\item[-] $\forall\Sigma, PM_3.S(\Sigma)=PM_1.S(\Sigma)\times PM_2.S(\Sigma)$
    \item[-] $PM_3.I=PM_1.I\cup PM_2.I-PM_1.O\cup PM_2.O$
    \item[-] $PM_3.O=PM_1.O\cup PM_2.O-PM_1.I\cup PM_2.I$
    \item[-] $PM_3.s_0=(PM_1.s_0, PM_2.s_0)$
    \item[-] $\forall\Sigma, PM_3.\delta(\Sigma)((s_1,s_2), i)=$
      \begin{displaymath}
        \left\{
        \begin{array}[h]{ll}
          q_d & s=q_0\land i=(A:d,B:\rnoread) \\
          q_d & s=q_{d'}\land i=(A:d,B:\rread) \\
          q_0 & otherwise \\
        \end{array}
        \right.
      \end{displaymath}
    \item[-] $\forall\Sigma, PM_3.\lambda(\Sigma)((s_1,s_2),i)=$
      \begin{displaymath}
        \left\{
        \begin{array}[h]{ll}
          q_d & s=q_0\land i=(A:d,B:\rnoread) \\
          q_d & s=q_{d'}\land i=(A:d,B:\rread) \\
          q_0 & otherwise \\
        \end{array}
        \right.
      \end{displaymath}
  \end{itemize}
\end{definition}

>>>>

So far as we can tell, most
works\cite{DBLP:conf/fase/RaffeltS06, DBLP:journals/corr/ChenHLLTWW15} on automata learning are not
capable of infinite models. \todo{reason?} Considering the semantics defined in section
\ref{sec:reo}, it's apparent that every finite connector has a corresponding constraint
automata, and the automata is also finite. Unfortunately, when checking the further definition of
Reo connectors' input, we find that it's not the case.

@@

\todo{finish the definition ..}
\begin{definition}[Production of Parameterized Mealy Machines]
  Now we're going to define the production operator \emph{prod} of two parameterized mealy machines as,
  \[
  prod(PM_1,PM_2)=PM_3
  \]
  as follows. Here we assume that $PM_2.O\cap PM_1.I=\varnothing$
  \begin{itemize}
  	\item[-] $\forall\Sigma, PM_3.S(\Sigma)=PM_1.S(\Sigma)\times PM_2.S(\Sigma)$
    \item[-] $PM_3.I=PM_1.I\cup PM_2.I-PM_1.O$
    \item[-] $PM_3.O=PM_1.O\cup PM_2.O-PM_2.I$
    \item[-] $PM_3.s_0=(PM_1.s_0, PM_2.s_0)$
    \item[-] $\forall\Sigma, PM_3.\delta(\Sigma)((s_1,s_2), i)=$
      \begin{displaymath}
        \left\{
        \begin{array}[h]{ll}
          (Out_1 + Out_2)|_{PM_3.O} & \rblock\land Out_2\neq\rblock \\
          \rblock & otherwise \\
        \end{array}
        \right.
      \end{displaymath}
      where we have
      \begin{itemize}
        \item[*] $In_1 = i|_{PM_1.I}$
        \item[*] $Out_1 = PM_1.\delta(\Sigma)(s_1,In_1)$
        \item[*] $In_2 = (Out_1 + i)|_{PM_2.I}$
        \item[*] $Out_2 = PM_2.\delta(\Sigma)(s_2,In_2)$
      \end{itemize}
    \item[-] $\forall\Sigma, PM_3.\lambda(\Sigma)((s_1,s_2),i)=(s_1',s_2')$
      where we have
      \begin{itemize}
        \item[*] $s_1' = PM_1.\lambda(\Sigma)(s_1,In_1)$
        \item[*] $s_2' = PM_2.\lambda(\Sigma)(s_2,In_2)$
      \end{itemize}
  \end{itemize}
\end{definition}
